%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------

  \cventry
    {Graduate Research Assistant} % Job title
    {Siebel School of Computing and Data Science, UIUC} % Organization
    {Urbana, Illinois} % Location
    {Aug 2024 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
      %\item Working on Low-Latency Networking, re-imagine the network stacks to adapt to different applications' needs, treating packets with varying performance goals (latency, throughput and reliability) as distinct traffic classes instead of treating all packets the same.
      \item Worked on Low-Latency Networking, re-imagining the QoS (Quality of Service) of applications. End-host devices can significantly improve the QoS of applications without any support from the core network. Treating packets with heterogeneous performance goals differently on the end host leads to huge benefits in latency.
      \item Developing a real-time query-able database system for satellite images, solving problems of communication and make it fast and cost-effective.
      \item Worked on improving the usage of eBPF by bridging the language-verifier gap and analyzing the model of verifier using abstract interpretation.
      \end{cvitems}
    }

%---------------------------------------------------------

  \cventry
    {Advisor \& Consultant} % Job title
    {Freelance: Venture Capital \& Startups} % Organization
    {Remote} % Location
    {Jan 2023 - Aug 2024} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Work as a \textbf{deeptech expert} for \textbf{evaluating potential deals} for institutional and micro VC funds.}
      \item {Advise young startups and various portfolio companies on \textbf{technical architecture, product planning and hiring}.}
      %\item {In-depth \textbf{research on eBPF} along with \href{https://www.chajed.io/}{\textbf{Prof. Tej Chajed}} and \href{https://pages.cs.wisc.edu/~swift/}{\textbf{Prof. Michael Swift}} from \textbf{University of Wisconsin-Madison}}.
      \end{cvitems}
    }

%---------------------------------------------------------

  \cventry
    {Co-Founder and Chief Technology Officer} % Job title
    {NimbleEdge} % Organization
    {Bangalore, India} % Location
    {Mar 2021 - Feb 2024} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {\textbf{NimbleEdge is revolutionising the way world computes}, migrating compute from the cloud to the edge (or user) devices, i.e. capturing free real estate. We take care of complex things like the diversity of computing power, OS or communication mediums.}
        %\item {Designed the entire technology, product, infrastructure and growth strategy of the company from an idea.}
        \item {Raised a \textbf{pre-seed round of \$3.3 Million} from \href{http://www.neotribe.vc/}{\textbf{Neotribe Ventures}} (based out of Silicon Valley) \& \href{https://sistemaasiacapital.com/}{\textbf{Sistema Asia Capital}} as institutional investors.}
        \item {\textbf{Built the entire Technology} (Systems, Development and DevOps), \textbf{Content, Marketing} and \textbf{Human Resources team} from scratch.}
        \item {Brought in \textbf{OYO, Dream11 \& Glance (Inmobi) as clients} for the company, each having \textbf{scale of more than 100 Million Monthly Active Users}.}
        \item {Built the \textbf{NimbleNet (Peer-to-Peer communication SDK)}, our main product to be completely agnostic of any operating system \& architecture.}
        \item {Built the entire Infrastructure for our \textbf{Aggregating Service} (Cloud Service) to be able to handle \textbf{scale of 100s of Millions of devices}.}
        \item {Completed the Paid Pilot with OYO via A/B testing over 100 Thousand devices with incredible results in CTR improvement \& cloud cost reduction.}
        \item {Technologies focussed: C/C++, Golang, Scala, Distributed Edge Computing, Homomorphic Encryption, Peer-to-Peer Communication Protocols.}
        \item {Our clients are able to unlock the power of \textbf{Hyper-personalization - Billion models for Billion users} and access to untapped data with unlimited revenue potential. All this while \textbf{saving enormous cloud costs, improving performance and enhancing end user privacy}.}
      \end{cvitems}
    }

%---------------------------------------------------------

  \cventry
    {Low Latency Software Developer} % Job title
    {Tower Research Capital} % Organization
    {Gurgaon, India} % Location
    {Aug 2020 - Mar 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Write efficient and maintainable automated software in C++ allowing us to ensure our correct position in the market.}
        \item {Develop cutting-edge software in C++ and Python which allow trading teams to run strategies smoothly.}
        \item {\textbf{Maintained the entire Trade Reconciliation System} along with a team of 2 people for all the markets that Tower Research Capital trades on.}
        \item {\textbf{Expanded the Tower's Trading \& Reconciliation System} to allow trading \textbf{on Taiwan Futures \& Crypto Exchanges like FTX, Huobi}.}
        \item {\textbf{Developed low latency Simulation Software} in C++ and Python running within containerized environment for \textbf{testing out trading strategies and platform}. Simulated the trading with custom exchanges developed in-house using historical market data.}
      \end{cvitems}
    }

%---------------------------------------------------------

  \cventry
    {Co-Founder and Chief Technology Officer} % Job title
    {InterviewVector} % Organization
    {Gurgaon, India} % Location
    {June 2020 - Aug 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {InterviewVector \textbf{created Interview as a Service (IaaS) category} helping companies in hiring for Technical roles across teams.}
        \item {We believe Engineers' precious time is better spent churning out the next big feature, not on taking interviews to weed out the unfit candidates.}
        %\item {We had an expert panel of experienced interviewers to handle screening rounds for the companies, It's cost-effective! It's quick. It's scalable.}
        \item {Signed \textbf{more than 10 clients} including emerging unicorns \textbf{like BharatPe \& MindTickle in first 3 months}.}
        \item {\textbf{Bootstrapped} the business to an \textbf{ARR of \$170,000 in just 4 months}.}
        %\item {Continued as a Consultant \& Advisor.}
      \end{cvitems}
    }

%---------------------------------------------------------

  \cventry
    {Software Developer Intern} % Job title
    {Eightfold.ai} % Organization
    {Noida, India} % Location
    {Apr 2020 - June 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Configured and deployed the \textbf{complete Alert Management System for the production \& development environment}.}
        \item {\textbf{Re-designed the complete product model} to facilitate and \textbf{setup Behavior Driven Development style of testing} using Selenium Framework.}
        \item {Reduced the \textbf{time taken to run the complete test suite from 62 minutes to less than 10 minutes (84\%)}.}
        %\item {Developed and enhanced the experience of the chatbot as part of the personalized career site product.}
      \end{cvitems}
    }

%---------------------------------------------------------

  \cventry
    {Software Developer Intern} % Job title
    {Core Engineering, Tower Research Capital} % Organization
    {Gurgaon, India} % Location
    {May 2019 - July 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Containerized and automated Trade Reconciliation setup to run as microservices on bare metal Kubernetes.}
        \item {Developed low latency software in C++ to facilitate integration and regression testing of Trade Reconciliation setup by inducing "deterministic mutations" on the network stream to simulate diverse un-reconciliation or trading-platform failure scenarios.}
        %\item {Creation of integration testing setup allowed prevention of diverse trading-platform failure scenarios saving a lot of money and time.}
        \item {Received a Pre-Placement Offer even though there was no vacant position, out of \textasciitilde 35 interns.}
%        \item {Developed tools to Simulate \textbf{Deterministic Chaos} for Integration Testing of different components.}
      \end{cvitems}
    }

%---------------------------------------------------------

  \cventry
    {OpenPrinting, The Linux Foundation} % Job title
    {Google Summer of Code} % Organization
    {} % Location
    {May 2018 - August 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        %\item {Worked on the Common Print Dialog Project, developing backend to print to a file and ``GTK3" adaptor backend connecting various Common Print Dialog backends installed at the time serving all available printers to the Common backend.}
        \item {Worked on the Common Print Dialog Project, developing backend connecting and serving all available printers to the Common backend.}
        \item {The Dialog allowed access to the available printing queues such as "CUPS", "Google Cloud Print" and more via "Dbus" on the network/system.}
        %\item {The Common Print Dialog allowed access to the printing queues of diverse applications without the need to install separate softwares for each.}
%        \item {Worked on developing backend for printing to a file.}
%        \item {Worked on developing GTK3 adaptor backend connecting all CPDB backends which are currently installed.}
%        \item {Technologies used: CUPS, GTK3, Dbus}
      \end{cvitems}
    }

%---------------------------------------------------------

  \cventry
    {Infrastructure Management \& Full Stack Developer, Supervisor Prof. Manindra Agrawal} % Job title
    {New York Office, IIT Kanpur} % Organization
    {Kanpur, India} % Location
    {May 2017 - Mar 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
%        \item {Summer Internship continued as a volunteer and peer mentor.}
        \item {Worked on a scalable microservice based web application with an extensive technology stack.}
        %\item {Designed and developed critical backend features while ensuring type-safety.}
        \item {Developed and deployed the data sharing functionality (using Kafka, Redis, Scala and Go).}
        \item {Deployed microservices utilizing Docker, Coreos Container Linux, ConcourseCI, JenkinsCI, and have maintained the cluster on Kubernetes.}
        \item {Configured and deployed complete Persistent Volume Storage System, ConcourseCI and pipelines for diverse microservices.}
%        \item {Configured and deployed the ConcourseCI and pipelines for different microservices.}
        \item {Developed and deployed LeaderBoard, an Automated Ranking and Scoring System using Ruby on Rails.}
        \item {Technologies used: Kubernetes, Docker, Kafka, JenkinsCI, Ruby on Rails, Nginx, Coreos Applications, Rook with Cephfs, Glusterfs.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
