% ----------------------------------------------------------------------------------------
% SECTION TITLE
% ----------------------------------------------------------------------------------------
\cvsection{Positions of Responsibility}

% ----------------------------------------------------------------------------------------
% SECTION CONTENT
% ----------------------------------------------------------------------------------------

\begin{cventries}

  \extraentry
  {Department of Computer Science and Engineering, IIT Kanpur}
  {Teaching Assistant}
  {IIT Kanpur}
  {July 2019 - July 2020}
  {
    \begin{cvitems}
      \item Tutored multiple groups of 40 students in basics of C programming, for the course ``Introduction to Programming".
      \item Designed and graded assignments, quizzes and exams for the course of \textasciitilde 1000 students.
    \end{cvitems}
  }

  \extraentry
  {IIT Kanpur}
  {System Administrator}
  {IIT Kanpur}
  {Mar 2018 - July 2020}
  {
    \begin{cvitems}
      \item Administered a cloud in IIT Kanpur, deploying and managing services for the campus community.
      \item Participating in (and Organising) Capture the Flag contests.
    \end{cvitems}
  }

  \extraentry
  {Programming Club, IIT Kanpur}
  {Coordinator}
  {IIT Kanpur}
  {Mar 2018 - Feb 2019}
  {
    \begin{cvitems}
      \item Organized, and set problems for various capture the flag and programming contests on campus.
      \item Conducted lecture series and workshops on programming topics.
      \item Organized the Summer Camp \& the Winter Camp, and mentored over 50 students in various topics who completed projects in distinct fields.
      \item Mentored 12 students in building IoT applications using Amazon Echo/Alexa and Google Home as a Semester Project.
    \end{cvitems}
  }

  %\extraentry
  %{Developer Students Club, IIT Kanpur, Google Developers}
  %{Leader}
  %{IIT Kanpur}
  %{July 2017 - Present}
  %{
  %}
  %\vspace{-0.3cm}
  %\extraentry
  %{Programming Club, IIT Kanpur}
  %{Secretary}
  %{IIT Kanpur}
  %{Apr. 2017 - Feb. 2018}
  %{
  %}

\end{cventries}
