%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template for Cover Letter
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Authors:
% Claud D. Park <posquit0.bj@gmail.com>
% Lars Richter <mail@ayeks.de>
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%


%-------------------------------------------------------------------------------
% CONFIGURATIONS
%-------------------------------------------------------------------------------
% A4 paper size by default, use 'letterpaper' for US letter
\documentclass[11pt, a4paper]{awesome-cv}

% Configure page margins with geometry
\geometry{left=1.4cm, top=.8cm, right=1.4cm, bottom=1.8cm, footskip=.5cm}

% Specify the location of the included fonts
\fontdir[fonts/]

% Color for highlights
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight
\colorlet{awesome}{awesome-red}
% Uncomment if you would like to specify your own color
% \definecolor{awesome}{HTML}{CA63A8}

% Colors for text
% Uncomment if you would like to specify your own color
% \definecolor{darktext}{HTML}{414141}
% \definecolor{text}{HTML}{333333}
% \definecolor{graytext}{HTML}{5D5D5D}
% \definecolor{lighttext}{HTML}{999999}

% Set false if you don't want to highlight section with awesome color
%\setbool{acvSectionColorHighlight}{true}

% If you would like to change the social information separator from a pipe (|) to something else
\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad}


%-------------------------------------------------------------------------------
%	PERSONAL INFORMATION
%	Comment any of the lines below if they are not required
%-------------------------------------------------------------------------------
% Available options: circle|rectangle,edge/noedge,left/right
\name{Ayush}{Bansal}
\position{Founder, \href{http://www.catb.org/~esr/faqs/hacker-howto.html\#what\_is}{Hacker}, Musician, Geek}
\address{Wired in{\enskip\cdotp\enskip}Bangalore, Karnataka{\enskip\cdotp\enskip}Kota, Rajasthan}

\mobile{(+91) 94625-45882}
\email{ayushb268@gmail.com}
\homepage{ayushb.org}
\github{ayush268}
\linkedin{ayush268}
% \gitlab{gitlab-id}
% \stackoverflow{SO-id}{SO-name}
\twitter{AyushBansal26}
% \skype{ayushb268@gmail.com}
% \reddit{reddit-id}
% \extrainfo{extra informations}

\quote{``Explore life as if you were to die tomorrow! Learn as if you were to live forever! Carpe Diem!"}

%-------------------------------------------------------------------------------
%	LETTER INFORMATION
%	All of the below lines must be filled out
%-------------------------------------------------------------------------------
% The company being applied to
\recipient
  {}
  {}
% The date on the letter, default is the date of compilation
\letterdate{\today}
% The title of the letter
\lettertitle{Job Application for Quant Developer}%TODO}
% How the letter is opened
\letteropening{Dear Sir/Ma'am,}
% How the letter is closed
\letterclosing{Sincerely,}
% Any enclosures with the letter
%\letterenclosure[Attached]{Curriculum Vitae}


%-------------- -----------------------------------------------------------------
\begin{document}

% Print the header with above personal informations
% Give optional argument to change alignment(C: center, L: left, R: right)
\makecvheader

% Print the footer with 3 arguments(<left>, <center>, <right>)
% Leave any of these blank if they are not needed
\makecvfooter
  {}
  {Ayush Bansal~~~·~~~Cover Letter}
  {\thepage}

% Print the title with above letter informations
\makelettertitle

%-------------------------------------------------------------------------------
%	LETTER CONTENT
%-------------------------------------------------------------------------------
\begin{cvletter}

\lettersection{About Me}
  I have been into coding since 2016. When discussing areas in Computer Science, I am great at Systems (Distributed \& Embedded), Security, Architecture, and Networks. I spent my early years at Quant Trading Firms and Product Companies, even successfully building a deep-tech infrastructure startup from the ground up. Since my initial days of slogging, I explored every field of Computer Science I could get my hands on, from Theoretical to Systems to AI. One of my hobbies is keeping on top of things in the tech world.

  Apart from being a Hardcore Techie, I enjoy engaging in other disciplines to learn as much as possible. And thus, I developed a particular interest in trading during my time at Tower Research Capital. Having worked in diverse environments, I can quickly adapt to any work. Also, my experience makes me great at working as part of a team and my love for teaching in mentoring my peers. My hobbies are reading, music (I can play five musical instruments), painting, cooking, and traveling.

\lettersection{Why Virtu Financial?} %TODO
  Virtu Financial works on the cutting edge, has a fast-paced environment, and focusses on creativity. Even though trades are in huge volumes, they have a lean team working on problems around the board. The systems and algorithms dealing with such diverse securities and trading volumes pose many exciting and challenging issues. I want to be a part of that.

Three essential things that attract me to Algorithmic Trading Firms are
  \begin{itemize}[noitemsep,topsep=0pt]
    \item the people around us,
    \item the challenging plus fast-paced environment/work with significant visible impact, and
    \item ofcourse pay.
  \end{itemize}
  During my time at Tower Research Capital, the people I worked with were like-minded, making it very comfortable and rewarding. Even the teams we work with are small, unlike Product Companies. It feels like a startup with exciting problems to solve every day. Thus, I want to work here after trying different sectors and companies.

\lettersection{Why Me?}
My passion, expertise \& experience in low latency systems is a huge plus point. I enjoy working on challenging technical problems even in my free time; my love for technology comes here. And I am a swift learner and adapt to any environment, which gives me a great headstart on any work I take up.

My prior experience at Tower Research Capital, Eightfold.ai, and building my startup has helped me gain great experience working as part of a team, adapting to changing environments, and even leading a team.

At Tower Research Capital, apart from working on the Trading Platform \& testing out trading strategies, I maintained their entire Trading \& Reconciliation System and even expanded it to enable trading on Taiwan FX \& Crypto Markets like FTX and Huobi. My experience here will be very beneficial.

\end{cvletter}


%-------------------------------------------------------------------------------
% Print the signature and enclosures with above letter informations
\makeletterclosing

\end{document}
